Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-11 submission/resp_to_revs_NatCom.tex
some edits to resp to revs

The first point is there are two things we are illustrating: one is when we increase both data size and model size (GPT2-small to GPT2-medium to GPT2-large to GPT2-xl); and the second is when a give model is trained to high-quality verus low-quality data (GPT2-small versus GPT).
For the former, we see a general trend with all the metrics decreasing, with the largest difference between GPT2-medium and GPT2-large, and with the difference between GPT2-small and GPT2-medium very small (near the noise level, and slightly in the opposite direction).
For the latter, we see GPT seems to violate what we expect. 
Thus, we look in more detail at the contributions to alpha-hat, i.e., to the PL exponent alpha and the spectral norm.
Doing this makes it clear what while the alpha part behaves as HT-SR theory would predict, i.e., with better models the PL exponents get smaller, the norms behave anomalously and exhibit scale collapes.
The bottom line is that the metrics we discuss can be sued to distinguish between well-trained versus very well trained models, but that one has to look at the PL exponents to diagnose gross model problems, which was one of our original points.
We have clarified these points
in the revised manuscript.

>>>>

The first point is there are two things we are illustrating: one is when we increase both data size and model size (GPT2-small to GPT2-medium to GPT2-large to GPT2-xl); and the second is when a given model is trained to high-quality verus low-quality data (GPT2-small versus GPT).
For the former, as the model size increases, we see a general trend with all the metrics decreasing, with the largest difference between GPT2-medium and GPT2-large, and with the difference between GPT2-small and GPT2-medium being very small (near the noise level, and slightly in the opposite direction).
For the latter, when comparing the well trained to poorly trained model, we see that the smaller and poorly trained GPT model seems to violate what we expect.
Thus, we look in more detail at the two contributions to alpha-hat, the PL exponent alpha and the spectral norm.
Doing this makes it clear what while the alpha part behaves as HT-SR theory would predict, and that with better models the PL exponents get smaller,
but the norms behave anomalously and exhibit scale collape.
The bottom line is that the metrics we discuss can be used to distinguish between well-trained versus very well trained models, but that one has to look at the PL exponents and Spectral Norm to diagnose the model problems; this was one of our original points.
We have clarified these points in the revised manuscript.
